Towards a Neural Co-Processor Which Restores Movement After Stroke: Modeling a Proof-of-Concept

### 2021-11-11 paper/article.tex
Paper progress

\begin{figure}
\includegraphics[width=\textwidth]{michaels.eps}
\caption{Michaels Modular RNN (mRNN), a simulated grasping circuit. The emergent dynamics of the
three modules correspond well to natural neural activity measured from primate AIP, F5, M1 regions,
respectively, from the same task. Visual (VGGNet) features forward propagate through the
network, conditioning the grasp for the object of the particular size, shape, and location.}
\centering
\label{fig:michaels}
\end{figure}

@@

\subsubsection{Simulated network exhibits long running dynamics}
Just as the co-processor must adapt to the lesion, it must also adapt to the dynamics of
the network it is stimulating. Natural neural networks as well as our stimulated network
exhibit long running dynamics, which our CPN and EN must account for in their learning.
A perturbation of a network (i.e. due to stimulation) will cause changes in neuron
activations long after the stimulation is applied, sometimes far from the site of
stimulation. Our simulated grasping circuit exhibits the same behavior.

@@

\subsection{Training the Co-Processor}
Alternate training EN and CPN.
\begin{itemize}
	\item Train an EN
		\begin{itemize}
			\item Training the EN until predictive power reaches a threshold, based on current task performance
			\item Training regime based on most recent CPN, similar CPNS (noise added to params), and white noise stimulation
			\item Single batch of data from applying current CPN set and white noise to the brain, EN fit to ``offline'' it over maining epochs
			\item Predictive power alone is not sufficient for use in training the CPN: we need to form the batch as above, otherwise training is unstable.
			\item White noise and noised params
			\item ** Learning instability
			\item ** Predictive power isn't enough
			\item ** Illustrate this
		\end{itemize}
	\item Train the CPN
		\begin{itemize}
			\item Backprop through the EN, effectively using the EN's prediction as ground truth
		\end{itemize}

>>>>

\begin{figure}
	\centering
	\begin{subfigure}[c]{0.69\textwidth}
		\centering
		\includegraphics[width=\textwidth]{michaels.eps}
		\caption{Michaels Modular RNN (mRNN), a simulated grasping circuit. The emergent dynamics of the
		three modules correspond well to natural neural activity measured from primate AIP, F5, M1 regions,
		respectively, from the same task. Visual (VGGNet) features forward propagate through the
		network, conditioning the grasp for the object of the particular size, shape, and location.}
	\end{subfigure}
	\hfill
	\begin{subfigure}[c]{0.30\textwidth}
		\centering
		\includegraphics[width=\textwidth]{mRNN_J.png}
		\caption{Connectivity matrix $J$. Note the within-module connections
		(on the diagonal) are fully connected, and connections to adjacent
		modules are sparse $10\%$.}
	\end{subfigure}
	\hfill
\caption{Architecture of the Michaels mRNN}
\label{fig:michaels}
\end{figure}

@@

\subsubsection{Simulated network exhibits long running dynamics}
Just as the co-processor must adapt to the lesion, it must also adapt to the dynamics of
the network it is stimulating. Natural neural networks as well as our simulated network
exhibit long running dynamics, which our CPN and EN must account for in their learning.
A perturbation of a network (i.e. due to stimulation) will cause changes in neuron
activations long after the stimulation is applied, sometimes far from the site of
stimulation. Our simulated grasping circuit exhibits the same behavior.

@@

\subsection{Training the Co-Processor}
In all experiments, training the co-processor requires a careful interleaving of
EN and CPN training epochs. EN training epochs concentrate on updating the EN,
based on observations of the effect of stimulation on the simulated network.
The loss function when training the EN is the MSE loss between the actual and
predicted output of the mRNN (i.e. muscle velocities). We then use the EN
to train the CPN during the CPN training epochs. During that time, we backpropagate
the MSE loss between the EN output, and target output, to the CPN. See Fig.
\ref{fig:training}.

TODO: explain EN training

\begin{figure}
	\centering
	\begin{subfigure}[c]{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{backprop_en.eps}
		\caption{EN training phase: backpropagate actual vs predicted}
	\end{subfigure}
	\hfill
	\begin{subfigure}[c]{0.48\textwidth}
		\centering
		\includegraphics[width=\textwidth]{backprop_cpn.eps}
		\caption{CPN training phase: backpropagate actual vs target MSE loss, via EN, to CPN. This effectively treats the EN output as the actual, and thus the EN must be trained first.}
	\end{subfigure}
	\hfill
\caption{Two Phase Training Regime}
\label{fig:training}
\end{figure}

\begin{itemize}
	\item Train an EN
		\begin{itemize}
			\item Training the EN until predictive power reaches a threshold, based on current task performance
			\item Training regime based on most recent CPN, similar CPNS (noise added to params), and white noise stimulation
			\item Single batch of data from applying current CPN set and white noise to the brain, EN fit to ``offline'' it over maining epochs
			\item Predictive power alone is not sufficient for use in training the CPN: we need to form the batch as above, otherwise training is unstable.
			\item White noise and noised params
			\item ** Learning instability
			\item ** Predictive power isn't enough
			\item ** Illustrate this
		\end{itemize}
	\item Train the CPN
		\begin{itemize}
			\item Backprop through the EN, effectively using the EN's prediction as ground truth
		\end{itemize}
